Outbreak Threshold Detection

### 2023-03-09 notebooks/Julia/simulation-detection.qmd
Update to Julia 1.9 release candidate 1

---
title: "Outbreak Threshold Detection"
author: "Callum Arnold"
date: today
title-block-banner: true
format:
  html:
    theme: flatly
    toc: true
    toc-depth: 4
    code-copy: true
    code-fold: true
    code-overflow: wrap
    code-tools: true
    code-link: true
    anchor-sections: true
    fig-width: 10
    fig-height: 8
execute:
  cache: true
jupyter: julia-1.8
---

>>>>

---
title: "Outbreak Threshold Detection"
author: "Callum Arnold"
date: today
title-block-banner: true
format:
  html:
    theme: flatly
    toc: true
    toc-depth: 4
    code-copy: true
    code-fold: true
    code-overflow: wrap
    code-tools: true
    code-link: true
    anchor-sections: true
    fig-width: 10
    fig-height: 8
execute:
  cache: true
jupyter: julia-1.9
---
